\section{Equality between metrics}

In this section, we prove our main theorems, Theorem~\ref{} and~\ref{}. That
is, we prove that the edge-squared metric exactly equals the nearest neighbor
metric on any point set, and that the $q$-edge power metric equals the $q$-NN
metric for any set of four points or less. We also conjecture that the $q$-edge
power metric always equals the $q$-NN metric. Even though the number of points
we handle for the general $q$-edge power metric is quite small, this still
represents progress; exactly computing the NN or $q$-NN metric even for four
points in two dimensions requires dealing with uncountably number of paths
through space. Furthermore, we provide a discrete criterion for testing whether
the $q$-NN metric equals the $q$-edge power metric, which may be useful for
future work.

Our tools for proving both theorems will be use of min-cost flows generated
from a conservative vector field. This is the core idea that lets us surmount
the difficulties in dealing with uncountably many paths. We hope that our ideas
may be more generally applicable to various metrics.

As seen in Section~\ref{}, it suffices to prove our equalities on the $q$-screw
simplex. As it turns out, the geometry of the $2$-screw simplex has very
elegant geometry. However, our techniques here may be appilcable to more
general configurations of points.

\subsection{Proof Strategy}

Given points $x_0, x_1, \ldots x_n$, our strategy is to build a graph $G'$ with
vertices $v_0, v_1, \ldots v_{n-1}$, and $v_S$ for any subset $S$ of
$\{0,1,2,3,4 \ldots n-1 \}$. Here, $v_S$ is a vertex representing the
circumcenter of the vertex set $\{x_s: s \in S\}$. Graph $G'$ then has some
edges (connected in a fashion to be detailed later), and costs on these edges.
Graph $G'$ is similar to the barycentric subdivision on a graph, used
in~\cite{}.

Tto lower bound any nearest neighbor path in our original point set, we will
lower bound it by some unit flow (DFEINE) from $v_0$ to $v_n$ in $G'$. However,
note that the unit flow from $v_0$ to $v_n$ is lower bounded by the shortest
path (where lengths of edges are the same as their costs) from $v_0$ to $v_n$
in $G'$. If the shortest path in $G'$ is equal to the $q$-edge power cost of
going from $x_0$ to $x_n$, then we have completed our proof.

To lower bound the cost of the $q$-NN metric with a unit flow, we aim to build
a potential function $\Conv:\mathbb{R}^n \rightarrow \mathbb{R}^{2^n}$ such
that $\Conv(p)$ is a vector whose entries sum to one. Here, $\Conv(p)$
represents a convex combination of the vertices of $G’$. We construct $\Conv$
such that $\Conv(v_S) = e_S$, where $e_S$ represents the unit vector with $1$
in the coordinate indexed by $S$, and $0$ elsewhere. Additionally, $\Conv$ has
the property that the $q$-NN cost of any path from $x \in \mathbb{R}^n$ to
$x+\Delta(x) \in \mathbb{R}^n$ (with respect to point set $x_0, \ldots x_n$) is
bounded below by the min cost flow on $G’$ satisfying demands
$\Conv(x+\Delta(x)) - \Conv(x)$. If we can construct such a function $\Conv$,
then the $q$-NN path from $v_0$ to $v_n$ is thus lower bounded by the min cost
unit flow from $v_0$ to $v_n$. Therefore, we have successfully lower bounded
the $q$-NN cost of a path from $x_0$ to $x_n$ with the shortest path in $G’$.

Therefore, the remainder of the section is devoted to two tasks: first,
constructing a $G’$ such that the shortest path in $G’$ is equal to the
$q$-edge power distance from $x_0$ to $x_n$. Second, constructing a function
$\Conv$ satisfying the properties listed above.

When $q = 2$, we can do this for any $n$, where $x_0, \ldots x_n$ form a
$2$-screw simplex. This will prove Theorem~\ref{}. When $q > 2$, we can do this
for any four points that are vertices of a $q$-screw simplex. This will prove
Theorem~\ref{}. We further conjecture our approach will work for any $q > 2$
and $n$.

\subsection{Construction of $G’$}

Let $G'$ be a graph on $\mathbb{R}^{2^n}$, with vertices $v_{S}$ for all $S
\subset \{0,1,\ldots n-1\}$. Connect vertices $v_S$ and $v_T$ for $S, T \subset
\{0, 1, \ldots n-1\}$ iff sets $S$ and $T$ differ by exactly one element. We
assign this edge a cost of $|R_{S}^q - R_{T}^q|$, where $R_{S}$ is the
circumradius of points $\{x_s : s \in S\}$.

\begin{lemma}\label{lem:flow}There exists a function $B'$, such that for any
path piece $\phi$ running from $x$ and $x+\Delta(x)$, $q-NN(\phi) \geq
MCF_{G'}(B'(x+\Delta(x))-B'(x))$. Here, $MCF_{G'}(d)$ for $d \in
\mathbb{R}^{2^n}$ represents the minimum cost flow on $G'$ satisfying demands
$d$ on the vertices of $G'$.

\end{lemma}

\begin{lemma}\label{lem:radius} Let $S = s_1 < s_2 < \ldots s_{|S|}$, and $T =
t_1 < \ldots \leq t_{|T|}$, where $S, T \subset \{0,1,\ldots n-1\}$ and $S$ and
$T$ differ by exactly one element. If

\begin{align}\label{eq:radius} |(R_{S})^q-(R_{T})^q| \geq
|(s_{|S|}-s_1)/2^q-(t_{|T|}-t_1)/2^q|, \end{align}

then the shortest path in $G'$ equals the shortest path in $G$.

\end{lemma}

Note that this inequality is always an exact equality for $q=2$. The proof of
this lemma is combinatorial:

\begin{proof}

\end{proof}

Therefore, if Equation~\ref{eq:radius} holds for any set of $k$ points, and
Lemma~\ref{lem:flow} and~\ref{lem:radius} are proven, then we've proven
Theorem~\ref{thm:general} for any $k$ element point set.

\textbf{Proof of Lemma~\ref{lem:flow}}

\textbf{Proof of Lemma~\ref{lem:radius}}

\begin{lemma} $SP_{G'}(v_0, v_n) \leq SP_G(x_0, x_n)$

\end{lemma}

\begin{proof}

The distance from $v_0$ to $v_{\{0,n-1\}}$ on the graph is equal to
$u_{n-1}-u_0$ (NORMALIZE THINGS PROPERLY, INDEX THINGS PROPER, SET COMMON
VARIABLE NAMES), and the distance from $v_{\{0, n-1\}}$ to $v_{n-1}$ is the
same. Thus, this path from $v_0$ to $v_n$ equals $SP_G(x_0, x_n)$, as the
latter is trivially equal to $u_{n-1} - u_0$.

\end{proof}

Thus, it suffices to prove that

\[ SP_{G'}(v_0, v_n) \geq SP_G(x_0, x_n) \]

%%%% GAP

\input{potential-construction}

Now, our proof will proceed in two parts. First, we construct a function
$B':\mathbb{R}^n \rightarrow \mathbb{R}^{2^n}$ assigning every point in
Euclidean space to a vector, representing a convex combination of vertices in
$G'$. We build $B'$ such that $B'(v_S)= e_S$, where $e_S$ is the unit vector
with $1$ in the dimension indexed by $S$. Next, we lower bound the
Nearest-Neighbor cost of an infinitesimal path piece. If the infinitesimal path
piece runs from $x \in \mathbb{R}^n$ to $x+\Delta(x)$, where both $x$ and
$x+\Delta(x)$ are in the same circumcentric subdivision (DEFINE), then we lower
bound it with some flow on the graph $G'$ satisfying demands $B'(x+\Delta(x)) -
B'(x)$.

If we can find a cost function $B'$ with these properties, we can integrate
over all the infinitesimal path pieces to show that the $p$-NN cost of a path
from $x_0$ to $x_{n-1}$ is lower bounded by some flow on $G'$. This is a unit
flow from $x_0$ to $x_n$. If we furthermore have that the shortest path on $G'$
equals the shortest path on $G$, then we have:

$$NN(path) \geq Q' \geq SP_{G'}(v_0, v_n) = SP_{G}(x_0, x_n).$$

Here, $Q'$ represents the cost of some flow from $v_0$ to $v_n$ on $G'$. Here,
$SP_{G'}(v_0, v_n)$ is the shortest path from $v_0$ to $v_n$ on $G'$ and
$SP_G(x_0, x_n)$ is the shortest path from $x_0$ to $x_n$ on the q-edge power
graph of the $q$-screw simplex.

Our proof then consists of two parts: the first is finding a graph $G'$ and
showing $SP_{G'}(v_0, v_n) = SP_G(x_0, x_n)$ (STANDARDIZE INDICES). The second
is finding a function $B'$ satisfying our desired properties listed in our
strategy. In the remainder of this section, we build our graph $G'$ and
establish

a discrete, sufficient-but-not-necessary criterion for when $SP_{G'}(v_0, v_n)
= SP_G(x_0, x_n)$. Then we build a function $B'$ and prove that $NN(path) \geq
Q'$, where the path runs from $v_0$ to $v_1$.

We then show that this necessary-but-not-sufficient criterion holds for any $5$
point $q$-screw simplex, thereby showing that the $q$-edge power metric equals
the $q$-NN metric for all $5$ point sets. We further conjecture that this
criterion holds for any $n$ points, but the authors are currently unable to
prove it.

Therefore, we have provided a sufficient but not necessary criterion for which
the $q$-edge power metric equals the $q$-NN Metric on the $q$-screw simplex.
Furthermore

Then we establish a discrete criterion in which $G' \geq G$. We then prove this
criterion holds for all sets of $5$ points in arbitrary dimension, and
conjecture that it holds for all sets of $n$ points in arbitrary dimension.
